Adopting agile in the large: motivations, success factors and challenges

### 2014-05-13 journal/article.tex
Problems with enterprise or external QA

>>>>

% Problems with enterprise or external QA

In an enterprise setting quality assurance (QA) tasks will require effort beyond
the general agile convention of doing testing within a crossfunctional team. In
large development efforts the agile model may need to be extended to accomodate
additional testing [P31]. Organizations may have existing separate QA teams that
must be coordinated to work with development teams [P17, P30, P48]. Integrating
enterprise scale QA will pose some additional challenges to agile methods.

Full quality assurance of a system requires special testing such as performance,
load, and memory testing, but agile methods lacks focus on them [P17]. These
testing activities can not be done within boundaries of user stories, and
require more resources than teams can spare [P31]. As testing tasks overlap team
boundaries it is sensible having a separate teams for the tasks, but
coordination practice between specialized QA teams and development teams needs
to be defined [P28, P48].

Some cases reported on problems with lack of automated testing. For a large
system the lack of automated tests caused excess testing work and late discovery
of defects [P10, P11, P17].

Still one challenge in QA was the relationship to requirements engineering. The
QA functions were struggling if there was problems such as ambiguity or
ineffective breakdown of large requirements [P48]. In a waterfall model an
extended time was reserved for QA at the end of projects, which allowed to
retroactively resolve ambiguities in requirements [P5]. However, as agile
required QA work to be done incrementally with development problems with
ambiguity in requirements became an impediment to QA [P5].
